This section contains reflections for each group member. These reflections
discuss how each group memeber felt the project went, and what they would do
different if they had to do it over again.

\subsection{Sam}

Reflection.

\subsection{Tadhg}

Reflection.

\subsection{Jason}

Overall, I think our project went ok, especially considering how bad it could
have gone. I felt that the project was risky from the start because a large
component of it is hardware design. There was very little room for error in the
board design because we only had time for one revision, manufacturing times
and component availability were out of our control, and simple mistakes in board 
design or assembly could have damaged many components wasting time and money. 
The COVID situation only made things more complex because we lost some of our 
backup plans for board assembly and could not easily work together on hardware 
development, debugging, and testing. All of that being said, I think we did a 
very good job of adapting and overcoming the issues we faced despite the cards 
not being in our favour. I was aware of all of these potential problems going
into the project, but I enjoy hardware development and was confident in our 
abilities so I was willing to take on the risk. What I did not foresee was the
software component of the project lagging behind as much as it did. I had no
worries about the software development at the beginning of the project 
because I thought it was very low risk, but by the end of the project it was
clear that I was wrong. I was not as involved with software development as I was
with hardware development so I am not the best person to say what we should 
have done different, but I think using a microcontroller that at least one of us
was familiar with would have helped. One thing we could have done differently to 
make hardware development much easier would be to make an entirely different 
project that does not depend on obscure sensors. Many of the sensors used in the 
project have little to no alternatives, and they tend to come in small packages 
that are hard to work with. We also could have made it easier by making 
something where size is not as relevant as it is in a watch.

\subsection{Morgan}

Reflection.