We created an initial timeline for our proposal which was revised for the
progress report.  Then finally we created a final timeline that reflects what
has actually occurred.  All three timelines are available in appendix
section \ref{sec:appendix-timelines}.

Our original timeline was very optimistic and ending up changing quite
dramatically.  Figure \ref{fig:proposal-final-timeline} shows the changes that
occurred.

Software development was started much later than intended. There are a few
explanations for this.  The software development environment was more difficult
to set up than expected as discussed in section \ref{sec:toolchain-issues}.
Furthermore, there was a discouraging lack of feedback since there was no
hardware to test on.

The most prominent change in hardware is the elimination of a second PCB
revision. Thankfully, only having one revision did not prevent us from making a
functional product, but this eliminate was done to save time, not because we
had a flawless first PCB revision.

The enclosure was delayed due to hardware assembly and part availability
issues.  The idea behind the enclosure design was to rapidly iterate the case
with the PCB in hand.  However, assembly and part availability issues meant the
hand off of the PCB to the case designer happened much later than expected.


\ganttset{
    calendar week text={\currentweek},
    y unit title=0.5cm, y unit chart=0.5cm,
    vgrid,
    x unit = 1mm,
    time slot format=isodate,
    time slot unit=day,
    title/.append style={draw=none, fill=RoyalBlue!50!black},
    title label font=\sffamily\scriptsize\color{white},
    title label node/.append style={below=-1.6ex},
    title left shift=.05,
    title right shift=-.05,
    title height=1,
    bar height=.6,
    group right shift=0,
    group top shift=.6,
    group height=.3,
    group peaks height=.2,
    bar incomplete/.append style={fill=Maroon},
    bar label node/.style={text width=3cm,align=right,font=\scriptsize\RaggedLeft,anchor=east},
    milestone label node/.style={text width=2cm,align=right,font=\scriptsize\RaggedLeft,anchor=east},
    group label node/.style={text width=3cm,align=right,font=\textbf\scriptsize\RaggedLeft,anchor=east},
    bar/.append style={opacity=0.5}
}

\newcommand\mygantttitle {
    \gantttitlecalendar{year} \\
    \gantttitlecalendar{month} \\
    \gantttitlecalendar{week}
}

\newcommand\proposalColor{blue!70}
\newcommand\progressColor{red!70}
\newcommand\finalColor{green!70}

\newcommand\proposalBar[3]
{\ganttbar[bar/.append style={fill=\proposalColor}]{#1}{#2}{#3}}
\newcommand\progressBar[3]
{\ganttbar[bar/.append style={fill=\progressColor}]{#1}{#2}{#3}}
\newcommand\finalBar[3]
{\ganttbar[bar/.append style={fill=\finalColor}]{#1}{#2}{#3}}

\newcommand\ProposalProgressBar[5]
{\proposalBar{#1}{#2}{#3}\progressBar{}{#4}{#5}}

\newcommand\ProgressFinalBar[5]
{\progressBar{#1}{#2}{#3}\finalBar{}{#4}{#5}}

\newcommand\ProposalFinalBar[5]
{\proposalBar{#1}{#2}{#3}\finalBar{}{#4}{#5}}

\begin{figure}[!htb]
\makebox[\textwidth][r]{
\begin{ganttchart}[]{2020-11-02}{2021-03-20}
    \mygantttitle \\
% Software
    \ganttgroup{Software}{2020-11-02}{2021-03-08} \\
    \ProposalFinalBar{Setup Dev. Env.}{2020-11-02}{2020-11-07}{2020-11-02}{2020-12-24} \\
    \ProposalFinalBar{USB Debugging Interface}{2020-11-08}{2020-12-19}{2020-12-25}{2021-01-22} \\
    \ProposalFinalBar{SD Card Driver}{2020-11-08}{2021-01-02}{2021-01-15}{2021-02-01} \\
    \ProposalFinalBar{Sensor Drivers}{2020-11-08}{2021-01-09}{2021-01-20}{2021-03-05} \\
    \ProposalFinalBar{Filesystem}{2020-12-12}{2021-01-16}{2021-01-22}{2021-02-19} \\
    \ProposalFinalBar{Bluetooth Interface}{2020-12-19}{2021-01-30}{2021-01-29}{2021-02-26} \\
    \ProposalFinalBar{Data Logging}{2020-12-26}{2021-01-30}{2021-02-05}{2021-02-19} \\
    \ProposalFinalBar{Companion Software}{2021-01-02}{2021-02-20}{2021-02-12}{2021-03-08} \\

% Testing
    \ProposalFinalBar{Sensor Driver Tests}{2021-01-09}{2021-02-13}{2021-02-05}{2021-03-08} \\

% Elec
    \ganttgroup{Hardware}{2020-11-02}{2021-03-06} \\
    \ProposalFinalBar{Electrical Schematic}{2020-11-02}{2020-12-12}{2020-11-02}{2020-12-24} \\
    \proposalBar{PCB Rev. A}{2020-12-13}{2021-01-30} \\
    \proposalBar{PCB Rev. B}{2021-01-31}{2021-03-06} \\
    \finalBar{PCB Layout}{2020-12-24}{2020-12-31} \\
    \finalBar{PCB Assembly}{2021-01-20}{2021-02-27} \\

% Mech
    \ganttgroup{Enclosure}{2021-02-01}{2021-03-15} \\
    \ProposalFinalBar{Enclosure Prototype}{2020-11-02}{2020-12-19}{2021-02-01}{2021-02-27} \\
    \proposalBar{Enclosure Prototype B}{2021-01-23}{2021-02-03} \\
    \ProposalFinalBar{Final Enclosure}{2021-02-27}{2021-03-08}{2021-03-05}{2021-03-15} \\
\end{ganttchart}
}
\begin{itemize}
    \item \colorbox{rgb:\finalColor,1;white,1}{Final Timeline}
    \item \colorbox{rgb:\proposalColor,1;white,1}{Proposal Timeline}
    \item \colorbox{rgb:\proposalColor,1;\finalColor,2;white,2}{Overlap}
\end{itemize}
\caption{Final timeline changes from proposal}
\label{fig:proposal-final-timeline}
\end{figure}
